---
output: 
  word_document: 
    reference_docx: word-styles-reference-01.docx
---

```{r, echo=FALSE, message=FALSE}
library(flextable)

duration_table <- readRDS(here::here('data_outputs/duration_table.RDS'))

driver_cats <- read_csv(here::here("data//driver_cat_desc_lookup.csv"))

apriori_bioregion_count <- readRDS(here::here('data_outputs/apriori_bioregion_count.RDS'))

```


**Table S1.** Frequency of time-series with short, moderate, and long time-series. 
The proportion of total time-series and studies (%) is show next to the count in 
parentheses. 

```{r, echo = FALSE}

duration_table %>% 
  mutate(site_col = paste0(sites, " (", site_prop, ")")) %>% 
  mutate(study_col = paste0(studies, " (", study_prop, ")")) %>% 
  select(duration_bin, site_col, study_col) %>% 
  flextable::flextable() %>% 
  flextable::set_header_labels(
    values = c(duration_bin = 'Duration (years)', 
               site_col = 'Number of time-series\n(proportion %)', 
               study_col = 'Number of studies\n(proportion %)')) %>% 
  theme_booktabs() %>% 
  # hline(i = 1, j = 1:5, border = officer::fp_border(width = 2), part = "header") %>% 
  # hline(i = 1, j = 2:5, border = officer::fp_border(width = 1), part = "header") %>% 
  # hline(i = 7, j = 1:5, border = officer::fp_border(width = 1), part = "body") %>% 
  #align(i = 1, j = 2:3, align = "center", part = "header") %>% 
  width(width = c(4, 5, 5) / cm(1))

```

<br>
<br>

<br>
<br>

**Table S2.** Distribution of a priori expectations of studies, as indicated by 
authors, across bioregions. Categories of ‘none’, ‘decrease’, ‘increase’, and 
‘other’ were made from author statements in the introduction of studies. The 
category ‘other’ captured U-shaped trajectories of declines then recovery.

```{r, echo=FALSE}
apriori_bioregion_count %>% 
  as_tibble %>%
  pivot_wider(names_from = apriori_cat, values_from = n) %>% 
  select(bioregion, none, decrease, increase, other) %>% 
  janitor::adorn_totals(name = "All regions") %>% 
  rename_all(str_to_sentence) %>%
  flextable::flextable() %>% 
  flextable::add_header_row(values = c('Bioregion', 'A priori category', '', '', '')) %>% 
  merge_at(i = 1, j = 2:5, part = "header") %>% 
  merge_at(i = 1:2, j = 1, part = "header") %>% 
  theme_booktabs() %>% 
  hline(i = 1, j = 1:5, border = officer::fp_border(width = 2), part = "header") %>% 
  hline(i = 1, j = 2:5, border = officer::fp_border(width = 1), part = "header") %>% 
  hline(i = 7, j = 1:5, border = officer::fp_border(width = 1), part = "body") %>% 
  align(i = 1, j = 2:5, align = "center", part = "header") %>% 
  width(width = c(6.5, 2, 2.5, 2.25, 2) / cm(1))

```

<br>
<br>

<br>
<br>

**Table S3.** Examples of the types of activities and environmental states 
assigned to the driver categories used in Figure 5.

```{r, echo=FALSE}
driver_cats %>% 
  select(driver_cat, examples) %>% 
  filter(driver_cat != "cumulative impact metric") %>%
  drop_na() %>% 
  mutate_all(str_to_sentence) %>% 
  arrange(driver_cat) %>% 
  rename("Driver" = driver_cat) %>% 
  rename_all(str_to_sentence) %>% 
  flextable::flextable() %>% 
  theme_booktabs() %>% 
  align(align = "left", part = "all") %>% 
  width(width = c(4.6, 12) / cm(1))
```